---
title: "p8108_hw6_yl4925"
author: "Yiming Li"
date: "12/3/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 8, 
  fig.asp = 0.8,
  dpi = 200,
  out.width = "90%",
  message = F,
  echo = T,
  warning = F)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(ggplot2.continuous.colour = "viridis",
        ggplot2.continuous.fill = "viridis")
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
```

```{r}
birthweight_df = read.csv("./data/birthweight.csv") %>% 
  janitor::clean_names() 
```

```{r}
birthweight_df %>% 
  filter(is.na(rowSums(birthweight_df)))
```
There is no missing value.

```{r}
fct_birthweight_df = birthweight_df %>% 
  mutate(babysex = case_when(
    babysex == 1 ~ "male",
    babysex == 2 ~ "female"
  ), frace = case_when(
    frace == 1 ~ "white",
    frace == 2 ~ "black",
    frace == 3 ~ "asian",
    frace == 4 ~ "puerto_rican",
    frace == 8 ~ "other",
    frace == 9 ~ "unknown",
  ), mrace = case_when(
    mrace == 1 ~ "white",
    mrace == 2 ~ "black",
    mrace == 3 ~ "asian",
    mrace == 4 ~ "puerto_rican",
    mrace == 8 ~ "other"
  )) %>% 
  mutate(babysex = fct_infreq(babysex), 
         frace = fct_infreq(frace),
         mrace = fct_infreq(mrace))
```

```{r}
original_fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + 
                    malform + menarche + mheight + momage + mrace + parity + pnumlbw + 
                    pnumsga + ppbmi + ppwt + smoken + wtgain, data = fct_birthweight_df)
```

```{r}
original_fit_df = original_fit %>% broom::tidy() 
original_fit_df %>% 
  filter(is.na(rowSums(select(original_fit_df, -term)))) %>% 
  select(term) %>% 
  knitr::kable()
```
We find there are three NA coefficients, which means that these three variables could be linear combination of other variables, so we do not choose these three variables as predictors.

```{r}
original_fit_df %>% 
  filter(p.value > 0.05) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable()
```
The p values for these 13 variables are greater than 0.05, which means that we could not reject null hypothesis (coefficient is zero). But for mrace variable, some values of this variable are necessary (p value < 0.05). So we remain these two variables and only exclude frace (only the p value for "unknown" < 0.05), fincome, malform, menarche, mheight, momage, ppbmi and ppwt.

```{r}
better_fit = lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace + 
                  parity + ppbmi + ppwt + smoken , data = fct_birthweight_df)
```

```{r}
better_fit %>% 
  broom::tidy()
```

```{r}
fct_birthweight_df %>% 
  modelr::add_residuals(better_fit) %>% 
  modelr::add_predictions(better_fit) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.5) + 
  labs(
    title = "lm_model residual VS prediction"
  )
```

```{r}
cv_df = 
  crossv_mc(fct_birthweight_df, 100) 
```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    my_mod = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace + 
                  parity + ppbmi + ppwt + smoken , data = .x)),
    len_ges_mod = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    headcir_len_sex_mod = map(train, ~lm(bwt ~ bhead + blength + babysex + 
                                           bhead * blength + bhead * babysex + blength * babysex + 
                                           bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_my = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
    rmse_len_ges = map2_dbl(len_ges_mod, test, ~rmse(model = .x, data = .y)),
    rmse_headcir_len_sex = map2_dbl(headcir_len_sex_mod, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs(
    title = "RMSE for three models"
  )
```

## problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
log_result_df = weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  mutate(term = case_when(
    term == "(Intercept)" ~ "beta0",
    term == "tmin" ~ "beta1"
  )) %>% 
  select(.id, term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  mutate(log = log(beta0 * beta1))
```

```{r}
log_result_df %>% 
  ggplot(aes(x = log)) +
  geom_density() +
  labs(
    x = "log(beta0 * beta1)",
    title = "Distribution of Estimates of log(beta0 * beta1)")
```
```{r}
log_result_df %>% 
  summarize(
    lower_limit = quantile(log, 0.025),
    upper_limit = quantile(log, 0.975),
    log_mean = mean(log),
    log_se = sd(log)) %>% 
  knitr::kable()
```

```{r}
r_square_result_df = weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(.id, r.squared)
```

```{r}
r_square_result_df %>% 
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(
    x = "r_squared",
    title = "Distribution of Estimates of r_squared")
```
```{r}
r_square_result_df %>% 
  summarize(
    lower_limit = quantile(r.squared, 0.025),
    upper_limit = quantile(r.squared, 0.975),
    r_square_mean = mean(r.squared),
    r_square_se = sd(r.squared)) %>% 
  knitr::kable()
```

